The increasing cost of happiness

### 2021-02-08 src/wdraft0.Rmd
Update to README

#### Model Selection

We compared the posterior evidence for a linear relationship between wellbeing and income with the posterior evidence of a nonlinear (piecewise) relationship (i.e., WAIC~linear~ — WAIC~piecewise~). Thus a WAIC difference greater than zero indicated evidence for a linear relationship. A WAIC difference less than zero indicated evidence for a nonlinear (piecewise) relationship.

##### Figure 2. Linear model evidence (WAIC~linear~ — WAIC~piecewise~)

```{r plot_waic_gh9}
waic_result <- read_rds("../results/model_comparisons_waic_R2_gh9.RDS")

waic_result %>%
  select(model, year, elpd_diff, se_diff) %>%
  filter(elpd_diff != 0) %>%
  filter(year %in% c(2002, 2006, 2010, 2014, 2018)) %>%
  rowwise() %>%
  mutate(samples = list(rnorm(n = 1e5, 
                              mean = elpd_diff * 2, # for pw advantage
                              sd   = se_diff *  2)),
         year = paste0("AD", year)
         ) %>%
  select(year, samples) %>%
  group_by(year) %>%
  unnest(samples) %>% 
  mutate(sample_id = c(1:1e5)) %>%
  pivot_wider(id_col = "sample_id", names_from = "year", values_from = "samples") %>%
  select(-sample_id) -> d2

color_scheme_set("red")

p5 <- mcmc_intervals(x = d2,
           pars = rev(colnames(d2)),
           prob = 0.00,
           prob_outer = 0.95
           ) +
  scale_x_continuous(
    limits = c(-200, 150)
    ) +
  geom_vline(aes(xintercept = 0), color = "grey90") +
  theme_test() +
  labs(
    subtitle = "Happiness")
```

```{r plot_waic_losat}
waic_result <- read_rds("../results/model_comparisons_waic_R2_losat.RDS")

waic_result %>%
  select(model, year, elpd_diff, se_diff) %>%
  filter(elpd_diff != 0) %>%
  filter(year %in% c(2002, 2006, 2010, 2014, 2018)) %>%
  rowwise() %>%
  mutate(samples = list(rnorm(n = 1e5, 
                              mean = elpd_diff * -2, # for linear advantage
                              sd   = se_diff *  2)),
         year = paste0("AD", year)
         ) %>%
  select(year, samples) %>%
  group_by(year) %>%
  unnest(samples) %>% 
  mutate(sample_id = c(1:1e5)) %>%
  pivot_wider(id_col = "sample_id", names_from = "year", values_from = "samples") %>%
  select(-sample_id) -> d1

# "fix" d1
colnames(d1) <- rev(colnames(d1))

color_scheme_set("blue")

p6 <- mcmc_intervals(x = d1,
  pars = colnames(d1),
  prob = 0.0,
  prob_outer = .95
  ) +
  scale_x_continuous(
    limits = c(-200, 150)
    ) +
  geom_vline(aes(xintercept = 0), color = "grey90") +
  theme_test() +
  labs(
    subtitle = "Satisfaction",
    x = "WAIC difference (95% interval)")
```

```{r figure_2, fig.width=6.5, fig.height=4, dpi=300}
p5 / p6
```

```
Figure 2 legend: Differences in posterior evidence for a linear fit over a piecewise fit (WAIC) for satisfaction (blue) and happiness (red). The filled circle indicates the mean of the distribution and the horizontal bars represents the 95% credible interval. A difference greater than zero is support for the linear model and a difference below zero is support for the piecewise model.
```

@@

Model selection revealed the posterior evidence for the linear fit of satisfaction on income was credibly superior to the nonlinear (piecewise) fit - Figure 2 shows the 90% credible interval of the fit for each year of satisfaction was above zero with no overlap. By contrast, a nonlinear fit of happiness on income was generally superior, and the nonlinear fit was credibly superior at 90% for each of three years (2006, 2014, 2018). Thus, the posterior evidence indicates happiness and satisfaction have distinct relationships with household income; satisfaction tends to increase linearly with income, while a change point exists in the relationship between happiness and income.

#### Parameter Estimation

Figure 3 below presents the complete posterior distribution of &omega; over 4000 samples drawn from the piecewise model, representing the location of the change point between happiness and household income in four separate years. Shaded areas to the right of the vertical grey dotted line are credibly (95%) larger than 2002. The figure shows the change point between happiness and household income (the _cost of happiness_) credibly increased between 2002 and 2018.

##### Figure 3. Posterior distributions of &omega; (95% distribution)  
```{r figure_3, fig.width = 6, fig.height = 4.5, dpi=300}
path_to_fits <- list.files(
  path = "../results",
  pattern = '^fit_cp_hifdip_gh9_cov_.*.RDS$',
  full.names = TRUE
)

posterior_alphas <- list()
for (pathtofile in path_to_fits) {
  df <- read_rds(pathtofile) %>%
    as.data.frame() %>%
    select(b_alpha_Intercept)

  colnames(df) <- paste0("param_", substring(pathtofile, 34, 37))

  posterior_alphas <- bind_cols(posterior_alphas, df)
}

posterior_alphas %>%
  mutate_all(.funs = ~brms::inv_logit_scaled(., 0, 100)*10) -> posterior_omegas

posteriors_trim <- posterior_omegas %>%
  mutate(
    param_2010 = (param_2010 + param_2011)/2,
    param_2003 = (param_2002 + param_2004)/2)

# select posteriors for plotting
posteriors_select <- posterior_omegas %>%
  select(param_2002, param_2006, param_2010, param_2014, param_2018)

color_scheme_set("red")

mcmc_areas_ridges(
  posteriors_select,
  pars = rev(colnames(posteriors_select)),
  prob = 0.95, 
  prob_outer = .99 
  ) +
  theme_test() +
  geom_vline(aes(xintercept = median(posteriors_select$param_2002)), 
             color = "gray", 
             linetype = 3) +
  labs(x = "Household income ($000s)")
```

```
Figure 3 legend: Posterior distribution of the change point parameter representing the location in household income ($) for each year. Shaded area represents the 90% credible region.
```

#### Income and happiness

##### Figure 4. Estimated happiness (SD units) at $50K/yr and $80K/yr from 2002-2018 
```{r figure_4, fig.width=7, fig.height=5, dpi=300}
predicted_fits <- list()
for (pathtofile in path_to_fits) {
  fit <- read_rds(pathtofile)

  ans <- model.frame(fit) %>%
    summarise_all(median)

  newdat = data.frame(
    dollars = c(5, ans[, "dollars"], 8),
    age = rep(ans[, "age"], 3),
    age_sq = rep(ans[, "age_sq"], 3),
    male = rep(ans[, "male"], 3), 
    grad = rep(ans[, "grad"], 3)
  )

  df <- fitted(fit, newdata = newdat) %>% 
    as_tibble() %>%
    mutate(
      Dollars = c("$50K", "\u03bc", "$80K"),
      year = as.numeric(substring(pathtofile, 34, 37)))

  predicted_fits <- bind_rows(predicted_fits, df)
}

predicted_fits %>%
  select(Estimate, Dollars, year) %>%
  filter(Dollars %in% c("$80K", "$50K")) %>%
  spread(Dollars, Estimate) %>%
  mutate(`$80K - $50K (∆)` = `$80K` - `$50K`) %>%
  gather(income, happiness, -year) %>%
  mutate(income = fct_relevel(income, "$50K", "$80K")) %>%
  ggplot(aes(x = year, y = happiness, color = income)) +
  geom_point(size = 4, alpha = 0.25) +
  geom_smooth(method = "loess", se = F, span = 3) +
  facet_wrap(~income) +
  labs(caption = "Source:     HILDA, University of Melbourne
                 Predicted happiness scores (SD unit) from piecewise regression on real household income", 
       x = "", y = "") -> p

@@

```
Figure 4 legend: The difference (∆) in happiness between individuals with a household income of $50K per year and a household income of $80K per year has increased since 2009.
```

Figure 5 presents house income levels weighted for the Australian population (by age, sex, marital status, labour force participation and region). It shows the cost of happiness increased faster than household income between 2002 and 2018. As a result, a smaller percentage of the Australian population in 2018 achieved a level of financial security on which their happiness was no longer dependent on their income, relative to 2002.

##### Figure 5.  
```{r figure_5, fig.width=7, fig.height=6, dpi=300}
# Tabulate against median income
happywealth %>%
  filter(!student) %>%
  filter(!top_hifdip) %>%
  select(year, xwaveid, income = hh_disp_inc_eq) %>%
  filter(year %in% 2002:2018) %>%
  mutate(
    year = paste0("param_", year),
    income = income/1000) %>%
  left_join(
    gather(
      summarise_all(posteriors_trim, 
                    list(median)), 
      year, 
      change_point
    )) %>%
  mutate(
    year = extract_numeric(year)
    ) %>%
  group_by(year) %>%
  summarise(
    `Median household income\n ($000s)` = round(median(income), 
                                                2),
    `Cost of happiness\n ($000s)` = round(mean(change_point), 
                                          2),
    `Individuals affording happiness\n (Population %)` = round(mean(income > mean(change_point))
                                                           *100,
                                                           1)
    ) %>%
  gather("key", "value", -year) %>%
  mutate(
    key = paste0(key, "\n"),
    key = fct_relevel(key, "Median household income\n ($000s)\n")) -> df.plot

df.plot %>%
  filter(year %in% c(min(year), 2018)) %>%
  mutate(
    val = as.character(
      if_else(str_detect(key, "afford"),
              paste0(round(value), "%"),
              paste0("$", round(value), "K"))),
    vpos = if_else(val %in% c("$49K", "$72K", "41%"), -0.75, 1.65),
    hpos = if_else(year == min(year), 0.3, 0.8)
    ) -> df.label

ggplot(df.plot, aes(x = year, y = value, color = key)) +
  # geom_point() +
  geom_line(aes(group = key), size = 2, alpha = 0.5) +
  # geom_smooth(aes(group = key), se = F, span = .5) +
  labs(title = "Income & happiness in Australia between 2002-2018",
       caption = "Source: HILDA sample, University of Melbourne
                  Real household income (modified OECD scale) weighted for the Australian population",
       x = "  ", y = "") +
  # geom_vline(aes(xintercept = 2009), color = "red", linetype = 3) +
  # geom_text(data = gfc.note, aes(x = 2009.5, y = 57, label = string),
  #           colour = "red", size = 3, hjust = "left") +
  geom_text(data = df.label,
            aes(label = val, vjust = vpos, hjust = hpos)) +
  expand_limits(y = c(22, 73)) +
  facet_wrap(~key) -> p

p.econ <- p + 
  labs(subtitle = "  ") +
  ggthemes::scale_color_economist() +
  ggthemes::theme_economist(base_family="Verdana", base_size = 8) +
  theme(legend.position = "none",
        strip.text = element_text(size = 10)
        )
p.econ
```

```
Figure 5 legend: Real household income has stagnated in Australia since 2009 (post GFC) while the cost of happiness has increased. Consequently fewer Australians have a household income exceeding the cost of happiness in 2018.
```

@@

We found the relationship between subjective wellbeing and household income was positive, but happiness and satisfaction had different (positive) relationships: Satisfaction increased linearly with income, while happiness increased rapidly up to a point after which further increments in income produced less change – this confirms the distinct effects of money in previous research [e.g., @howell2008relation; @kahneman2010high], and contributes rare evidence from the same sample. Furthermore, we report here for the first time that the change point between household income and happiness increased over time between 2002 and 2018, faster than inflation or the median household income.

We refer to the change point after which increases in income no longer produce similar increases in happiness as the cost of happiness. After this point, happiness is no longer as dependent on household income, and the economic security it represents. Presumably after this point further increases in happiness depend on other life factors (e.g., social connections). Life satisfaction on the other hand always increased with household income. The difference likely reflects the importance of a numerical dollar value (e.g., bank balance, house value) when cognitively appraising one’s life achievements, versus the relevance of that number to our everyday experience of joy and prevailing mood.

An implication of the increasing cost of happiness over the last sixteen years is that wealth inequality is driving increasing _inequities_ in wellbeing. In 2002, the cost point of happiness represented a 9% increase over median income, while in 2018 it represented a 42% increase over median income. This also represents a reduction from 44% to 26% in the proportion of people who have achieved a level of financial security beyond which their happiness no longer depends. Thus we can see that over time in the last sixteen years the happiness of more people, i.e., their everyday experience of joy and their prevailing mood, has depended on their material wealth.

Australia has low levels of income disparity relative to other OECD countries, and the Gini coefficient has not changed a great deal between 2002 and 2018 in the HILDA dataset [@australian2018rising]. A stable Gini coefficient shows income inequality has remained steady over the time period, and our results do not conflict with this conclusion. Rather what we are revealing is the effect of income inequality on happiness has increased over the same time period. So while income inequality has remained steady, it’s impact on wellbeing inequity has increased. We think this highlights the issue that while traditional measures of wealth and income inequality may be relatively stable and exhibit little change, their impact on wellbeing and health can still vary. As focus shifts from traditional wealth indicators towards wellbeing measures, findings such as this may become more prevalent.

Some recent studies have challenged either the notion that the positive effect of household income plateaus, or that the effect on happiness and satisfaction are distinct. In a nationally representative sample of 44,000 adult Americans in the General Social Survey (GSS), happiness continued to increase with household income, implying no change point existed between money and happiness [@twenge2020expanding]. The GSS asks a single item on happiness: “Taken all together, how would you say things are these days – would you say that you are very happy, pretty happy, or not too happy?” The form of this question is quite similar to the single item “life satisfaction” question in HILDA, as both request the respondent to cognitively evaluate their circumstances. By contrast, the nine items we selected to measure happiness covered a range of affect and focused on current feelings: e.g., “How much of the time during the past 4 weeks have you been a happy person?”. Critical differences in the operational definition of happiness seem likely to explain the distinct results observed here.

A second recent report from a survey of 1.7 million people representing 164 countries in the Gallup World Poll reported increases in household income were associated with change points in happiness and satisfaction [@jebb2018happiness], rather than distinct effects as we found. It may be that differences in the sparsity of the high income data in HILDA (for which extremely high income households are masked) explain the differences here. However including these individuals in our analysis did not change the linear effect between income and satisfaction observed here, and the weighted topcodes should have biased the result towards a change point. We also note a linear effect between income and satisfaction is consistent with the majority of earlier literature [@howell2008relation; @stevenson2013subjective].

As governments and policy-makers begin to focus on wellbeing, it will be critical to understand how traditional economic indicators such as household income, wealth inequality, and consumption interact with wellbeing and health. According to @frijters2020happy, coming up with a consensus to translate income into wellbeing features high on the wider wellbeing research agenda. Establishing the links between wealth, household income, wellbeing and health, and how inequalities in one drives inequities in the other, will be a critical step in that agenda.

>>>>

Figure 3 shows that, on average, happiness estimates improved for people with household incomes above \$72K when compared to 2002, as indicated by the average delta (smooth blue line) falling above zero on the right side of the plot. Conversely, people with household incomes below \$72K, on average, suffered a decrease in estimated happiness compared to 2002. And the greatest decrease in happiness occurred for people whose income levels were transliminal: that is, their income was above the changepoint in 2002 but the shift in the change point resulted in their income falling below the change point in 2018. Of course the obtained deltas are due to changes in all the parameters of the function, including the slope before and after the change point. However because this comparison was performed on the same individuals (i.e., from the 2018 survey), it held characteristics such as age, income, etc, constant that would otherwise be expected to change over time and possibly contribute to any difference in happiness distribution. In this way these results isolate the amount of change entirely due to the _evolution_ of the function between 2002 and 2018, and demonstrates how this has contributed to the unequal distribution of happiness between the rich and the poor over time.

@@

#### The increasing cost of happiness in Australia

A less hypothetical implication of the shifting change point in the relationship between income and happiness is that over time fewer people have an income that affords them happiness, which is (relatively) independent of their financial security. Assuming median income is also not increasing at a faster rate, any increase in the change point will reduce the number of people who fall above it over time. Figure 5 presents median household income levels weighted for the Australian population (by age, sex, marital status, labour force participation and geographical region). It also shows the change point between income and happiness increased faster than rises in median household income between 2002 and 2018. The third panel shows that as a result, a smaller proportion of the Australian population in 2018 had a household income above the changepoint than in 2002.

##### Figure 4. Rise in median income, change point, and population in Australia 2002-2018 
```{r figure_4, fig.width=7, fig.height=6, dpi=300}
trimmed_omega <- posteriors_omega %>%
      mutate(
        # param_2002 = (param_2001 + param_2002)/2,
        param_2003 = (param_2002 + param_2004)/2,
        # param_2004 = (param_2003 + param_2004)/2,
        # param_2005 = (param_2004 + param_2005)/2,
        # param_2006 = (param_2005 + param_2006)/2,
        # param_2007 = (param_2006 + param_2007)/2,
        # param_2008 = (param_2007 + param_2008)/2,
        param_2009 = (param_2008 + param_2009)/2,
        param_2010 = (param_2009 + param_2011)/2,
        # param_2011 = (param_2010 + param_2011)/2,
        # param_2012 = (param_2011 + param_2012)/2,
        # param_2013 = (param_2012 + param_2013)/2,
        # param_2014 = (param_2013 + param_2014)/2,
        # param_2015 = (param_2014 + param_2015)/2,
        # param_2016 = (param_2015 + param_2016)/2,
        # param_2017 = (param_2016 + param_2017)/2,
        # param_2018 = (param_2017 + param_2018)/2
        )

# Tabulate against median income
happywealth %>%
  filter(!student) %>%
  filter(!top_hifdip) %>%
  select(year, xwaveid, income = hh_disp_inc_eq, weights) %>%
  filter(year %in% 2002:2018) %>%
  mutate(
    year = paste0("param_", year),
    income = income/1000) %>%
  left_join(
    gather(
      summarise_all(trimmed_omega, list(median)), 
      year, 
      change_point
    )) %>%
  mutate(
    year = extract_numeric(year),
    over_change = income > change_point,
    weighted_over = over_change * weights
  ) %>%
  group_by(year) %>%
  summarise(
    `Median household income\n ($000s)` = round(median(income), 2),
    # `Median household income\n ($000s)` = round(matrixStats::weightedMedian(income, weights)),

    `Change point\n ($000s)` = round(mean(change_point), 2),

    `Population above change\n(%)` = round(
      sum(weighted_over) / sum(weights) *100)

    ) %>%
  gather("key", "value", -year) %>%
  mutate(
    key = paste0(key, "\n"),
    key = fct_relevel(key, "Median household income\n ($000s)\n")
    ) -> df.plot

df.plot %>%
  filter(year %in% c(min(year), 2018)) %>%
  mutate(
    val = as.character(
      if_else(str_detect(key, "Population"),
              paste0(round(value), "%"),
              paste0("$", round(value), "K"))),
    vpos = if_else(val %in% c("$49K", "$72K", "42%"), -0.75, 1.65),
    hpos = if_else(year == min(year), 0.3, 0.8)
    ) -> df.label

ggplot(df.plot, aes(x = year, y = value, color = key)) +
  geom_line(aes(group = key), size = 2, alpha = 0.5) +
  labs(caption = "Source: Real household income (modified OECD scale) weighted for the Australian population",
       x = "  ", y = "") +
  geom_text(data = df.label,
            aes(label = val, vjust = vpos, hjust = hpos)) +
  expand_limits(y = c(22, 73)) +
  facet_wrap(~key) -> p

p.econ <- p + 
  labs(title = "Income & happiness in Australia between 2002-2018",
       subtitle = " ") +
  ggthemes::scale_color_economist() +
  ggthemes::theme_economist(base_family="Verdana", base_size = 8) +
  theme(legend.position = "none",
        strip.text = element_text(size = 10)
        )

@@

```
Figure 4 legend: Real household income has stagnated in Australia since 2009 (post GFC) while the change point between happiness and income has increased. Consequently fewer Australians had an income that affords them happiness, which is independent of their financial security in 2018.
```

@@

We confirmed previous findings [e.g., @howell2008relation; @kahneman2010high], that the relationship between both types of subjective wellbeing with household income was positive but quite different over a 17 year period: Satisfaction increased linearly with income, while happiness increased rapidly up to a point after which higher levels of income were associated with less improvement. For the first time we have shown that this change point in the relationship between household income and happiness increased faster than inflation or the median household income over time between 2002 and 2018.

We refer to the change point after which increases in income no longer produce similar increases in happiness as the _cost of happiness_. After this point, happiness is no longer as dependent on household income, and the economic security it represents. Presumably after this point further increases in happiness depend more on other life factors (e.g., leisure time, social connections). Life satisfaction on the other hand appeared to show consistent increases with household income and we found no evidence of any change point. The difference may reflect the importance of a numerical dollar value (e.g., bank balance, house value) when cognitively appraising one’s life achievements, versus the relevance of that number to our everyday experience of joy and our prevailing mood.

An implication of the changing relationship between happiness and income since 2002 is that income inequality may be driving increasing inequities in wellbeing. This is demonstrated in Figure 3, where the difference in happiness between 2002 and 2018 increased for incomes above $72K/year and decreased for incomes below that level. The inequity was also highlighted in Figure 4 where the change point of happiness represented a 9% increase over median income in 2002, while in 2018 it represented a 42% increase over median income. This increase relative to median income also represented a reduction from 42% to 24% in the proportion of people whose income fell above the changepoint. Thus we can see that over the last sixteen years the difference in happiness between the rich and the poor has increased; while the proportion of people whose happiness no longer depends on their financial security has decreased.

Australia has low levels of income disparity relative to many other OECD countries, and the Gini coefficient has not changed a great deal between 2002 and 2018 [@australian2018rising]. A stable Gini coefficient shows income inequality has remained steady over the time period, and our results do not conflict with this conclusion. Rather what we are revealing is that even a static income distribution may have dynamic effects on happiness over time. We think this highlights the issue that while traditional measures of wealth and income inequality may be relatively stable and exhibit little change, their impact on wellbeing and health can still vary. As such, we believe these results may well have relevance to other developed nations in North America and Europe which have enjoyed stable economic growth overall, but have stagnating incomes, and declining happiness levels [@sachs2019world]. As focus shifts from traditional financial indicators towards health and wellbeing measures, findings such as this may become more prevalent.

Some recent studies have challenged either the notion that the positive effect of  income plateaus after some level, or that the effect on happiness and satisfaction are distinct [@killingsworth2021experienced; @twenge2020expanding; @jebb2018happiness]. Most recently the point has been made that experienced happiness continues to increase on a log scale with income and does not plateau after USD75,000 [@killingsworth2021experienced]. It is worth noting that log-linear models are typically used to investigate income effects, and we would agree that our data do not support a strict view of a "satiety" point or flat gradient between income and happiness which can persist on a log scale [@jebb2018happiness; kahneman2010high]. But log-linear models mask the fact that marginal dollars matter less the more one earns, which is what we observed for happiness here. Furthermore, log models [and more flexible additive models @jebb2018happiness] may produce a better fit, but will not provide a clear or a distinct change point allowing us to test a change in the marginal effect of income. And so one implication of our model choice is that the change in slope may be much smoother than implied by our model. We concede this point but would still contend the location of the change in slope will display a comparable shift over time, if it can be detected with certainty.

Past researchers have also argued there is no distinct relationship between income and the different forms of subjective wellbeing (e.g., happiness, satisfaction), and that income has the same impact on both constructs. It is rare for such research to directly test differences in the form of the function, usually instead inferring no difference after observing null results. One benefit of our model selection was the quantification of the posterior evidence for a linear over a nonlinear function (e.g., Figure S1, Supplementary Materials). That showed the evidence for a linear effect was clearly different between our two wellbeing variables, and the evidence for a linear function was also decreasing over time. It may be that with more recent data, or in the near future, there is no distinct function between income and the different wellbeing constructs. However it is also worth noting that the only meta-analysis conducted in this area, over ten years ago, also suggested the linear relationship between income and life satisfaction is stronger than that with happiness [@howell2008relation]. We would also note that a linear function between income and life satisfaction as we report here, is consistent with the majority of earlier research [@stevenson2013subjective]. In general, the importance of differences between the distinct constructs of subjective wellbeing will need to be adjudicated when deciding how to measure income effects.

As governments and policy-makers begin to focus on wellbeing, it will be critical to understand how traditional economic indicators such as household income, wealth inequality, and consumption interact with wellbeing and health. According to @frijters2020happy, coming up with a consensus to translate income into wellbeing features high on the wider wellbeing research agenda. Establishing the links between wealth, household income, wellbeing and health, and how inequalities in one drives inequities in the other, will be a critical step in the success of that agenda.

## Acknowledgements

This research was not supported by any funding.

## Author contributions

RWM analysed the data and wrote the paper. NK designed the analysis and wrote the paper. NG proposed the idea, planned the analysis, and wrote the paper.

## Competing interests

The authors declare no competing interests.

## Additional information

This paper uses unit record data from Household, Income and Labour Dynamics in Australia Survey [HILDA](https://melbourneinstitute.unimelb.edu.au/hilda) conducted by the Australian Government Department of Social Services (DSS). The findings and views reported in this paper, however, are those of the author[s] and should not be attributed to the Australian Government, DSS, or any of DSS’ contractors or partners. All code and scripts used in the analysis are available at https://github.com/datarichard/The-increasing-cost-of-happiness

[Supplementary information](supplementary.html){:target="_blank"} is available online.
